### 2018-02-11 Writing/Thesis/content/chapter-conclusion.tex
More writing

% Move from specific to general
% Use existing literature for confirmation, contradiction, comparison
% "Speak to introduction"
\chapter{Conclusion}
\label{sec:conclusion}
% Introductory restatement of research problems, aims / reseach question -> remin of problem + purpose and how addressed
In this thesis, the problem of predicting a ranking of classification algorithms for a new data set on the basis of meta features of the data set and past performances of the algorithms has been considered. Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed. The problem has been addressed by implementing to different approaches, regression-based and preference-based ranking. Both have been evaluated extensively against a baseline and an oracle.

@@

% Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
On the basis of these results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms. A practical application of these findings may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}. However, some additional work may have to be done in extension to this thesis in order for a sensible integration.

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% Has worked reasonably well -> extend evaluation

%- more careful training by hand-selecting datasets for training (but then aains is this really the real world anymore? But then again duplicates may be contained)

- use this to try to predict other measures (e.g. time needed)
- look at the loss curve + loss-time (log) curve
- further investigate the better solution
- integrate solution into other auto ml solution if sensible regarding time contraints for that solution (and accuracy)
-e.g. use A3R
- or runtime could be predicted separately by nn based on meta data \cite{DBLP:journals/corr/abs-1709-07615}
- adding feature pre-processing

% Extension of the tool
- better fitting of learning algorithms to meta data (more manual work, but of course consider danger of overfitting!

% Extended evaluation
- compare against other tools that rank r.g. the Jan van Rijn one
- deeper analysis of meta features, e.g. add some, remove some, consider trade-off time accuracy

% Use this for predicting different algorithms
So far, the evaluation of the tool has been confined to predicting algorithms for classification. Since this has been relatively successful, it could be tested whether similar predictions can also be made for other machine learning tasks like regression or clustering.

- hyperparameters neglected here, may include standard combinations in future work (or random ones)-> possible only if id by string
- use this for regression

an average baseline like used in speeding up algo select might be better

>>>>

% Move from specific to general
% Use existing literature for confirmation, contradiction, comparison
% "Speak to introduction"
\chapter{Conclusion}
\label{sec:conclusion}
% Introductory restatement of research problems, aims / reseach question -> remin of problem + purpose and how addressed
In this thesis, the problem of predicting a ranking of classification algorithms for a new data set on the basis of meta features of the data set and past performances of the algorithms has been considered. Being able to predict a ranking of such algorithms is desirable since this potentially speeds up and simplifies the process of algorithm selection, which is important due to a rapidly increasing amount of available data, and more importantly, data that is available but has not yet been analyzed. This problem has been addressed by implementing two different approaches, regression-based and preference-based ranking. Both have been evaluated extensively against a baseline and an oracle.

@@

% Practical applications / limitations: assess value / relevance / implications: What does it mean for theory, what for practice
On the basis of these results, it can be concluded that a causal connection exists between certain meta features of a data set and the predictive accuracy of classification algorithms for this data set, which can be exploited to a degree by regression models and label ranking models to predict a ranking of classification algorithms. A practical application of these findings, apart from the direct use as a ranker, may be to incorporate the implementation or parts of it in another Auto-ML tool as a search heuristic, similar to how some Auto-ML solutions like AUTO-SKLEARN already benefits from meta learning \cite{feurer2015efficient}. However, some additional work may have to be done in extension to this thesis in order for a sensible integration.

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression based approach using random forests, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Different sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features.

% More evaluation - loss - time & compare agains Jan van Rijn
Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}. In this regard it would also be interesting  to implement the loss - and time - loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.

% Use this for predicting different algorithms
Additionally, so far the evaluation of the tool has been confined to predicting algorithms for classification. Since this has been relatively successful, it could be tested whether similar predictions can also be made for other machine learning tasks like regression or clustering with the same approach by extending the tool to handling these functions. Also, one could try to include a few parameterized versions of algorithms, as so far only one variant of each classifier with standard hyperparameters has been used.

% Use this to predict other measure
In a similar manner to extending the algorithms for which a performance measure is predicted, one could use the tool to predict different performance measures. For this, the tool does not even need to be adapted, as it is agnostic to the semantics behind the measure it predicts, it only needs to be numeric. One possibility for this would be the prediction of build or prediction times of learning algorithms, or a measure that combines time and accuracy \cite{DBLP:journals/ml/AbdulrahmanBRV18}.

% Auto fitting
Depending on the fact whether one is willing to trade-off longer build and prediction times, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.

% Additional baseline
Last, it could be interesting to implement an additional baseline that averages ranks instead of counting how many times an algorithm is ranked first. This would help to determine if the surprising ranking returned by the best algorithm baseline (see Fig. \ref{tab:bestAlgorithmRanking}
) still holds when using a different baseline. Naturally this new baseline then could also be used to re-evaluate the implemented ranking concepts.

### 2018-02-11 Writing/Thesis/content/chapter-evaluation.tex
More writing

@@

% Evaluation Measures used & computed
As a ranking returned by this oracle represents the ideal solution,

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline. The baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the RMSE of predict performance values cannot bet computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, and come as close as possible to the correct ranking.

@@

% Gathering data sets from OpenML

% Generating base performance data
Performance Values acquired with 5 times MCCV
why decided to use these algorithms and not others

@@

\begin{landscape}
\begin{table}[h]
\centering
	\begin{tabularx}{23,7cm}{>{\hsize=3.4\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-13}
							 			& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 		& Min	& Max		& Mean		& Stdv	\\ \hline
		LinearRegression 				& -0.255 	& 0.896 		& 0.473	 	& 0.221 & 0 		& 86.667 	& 3.469	 	& 7.244 		& 0 		& 31.220 	& 1.267	 	& 3.011 	\\
		M5P				 				& -0.29 		& 0.870 		& 0.470	 	& 0.219 & 0 		& 82.353 	& 3.78	 	& 6.535 		& 0 		& 82.353 	& 1.508	 	& 4.757 	\\	
		RandomForest		 				& -0.281 	& 0.922 		& 0.495	 	& 0.228 & 0		& 60 		& 3.097 		& 5.745 		& 0 		& 34.634 	& 1.308	 	& 3.150 	\\	
		REPTree			 				& -0.229 	& 0.896 		& 0.412		& 0.213 & 0 		& 82.353		& 4.829	 	& 7.948 		& 0		& 34.634 	& 1.759	 	& 3.515 	\\	
		InstanceBased 					& -0.429 	& 0.870 		& 0.221	 	& 0.249 & 0 		& 82.353		& 5.401 		& 9.44 		& 0 		& 82.353 	& 3.62	 	& 8.540 	\\	
		InstanceBased\footnotemark{}		& -0.429 	& 0.887 		& 0.340	 	& 0.252 & 0 		& 98.367 	& 5.437 		& 10.323 	& 0 		& 82.353 	& 3.294	 	& 8.367 	\\	
		InstanceBased\footnotemark{}		& -0.429 	& 0.870 		& 0.335	 	& 0.249 & 0 		& 82.353 	& 5.382	 	& 9.402 		& 0 		& 82.353 	& 3.511	 	& 8.493 	\\	
		PairwiseComparison 				& -0.870 	& 0.576		& 0.014	 	& 0.234 & 0 		& 97.822 	& 9.762	 	& 13.135 	& 0 		& 82.353 	& 4.001	 	& 8.600 	\\	
		BestAlgorithm	 				& -0.437 	& 0.489 		& 0.057	 	& 0.159 & 0		& 82.353		& 6.480 		& 10.168 	& 0		& 82.353		& 3.420 		& 8.195 	\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Evaluation results with full meta data}
\end{table}

\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}
\end{landscape}

\begin{table}[h]
\hspace{-1cm}
	\begin{tabularx}{1.15\textwidth}{>{\hsize=1.4\hsize}X | >{\hsize=.84\hsize}X | >{\hsize=1.07\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X}
		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7} 
										& Mann-Whitney U & P-Value & Mann-Whitney U	& P-Value & Mann-Whitney U & P-Value \\ \hline
		LinearRegression 				& 186381.5 & 2.702E-109 & 126861.5 & 7.694E-12 & 129028.0 & 1.327E-13 \\
		M5P				 				& 186236.0 & 6.230E-109 & 118828.5 & 1.840E-6 & 126379.5 & 1.821E-11 \\
		RandomForest		 			& 187750.5 & 9.737E-113 & 128853.5 & 1.861E-13 & 129037.0 & 1.304E-13 \\
		REPTree			 				& 181228.0 & 8.094E-97 & 111850.0 & 0.003 & 118793.0 & 1.926E-6 \\		
		InstanceBased					& 142665.5 & 8.818E-28 & 109372.0 & 0.020 & 104279.0 & 0.311 \\
		InstanceBased\footnotemark{}	& 166460.5 & 2.583E-65 & 111940.5 & 0.003 & 109211.0 & 0.022 \\
		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
		PairwiseCom- parison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Significance of Results Regarding Kendall Rank Correlation Coefficient}
\end{table}

@@

\subsection{Build and Prediction Times}
\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=2.6\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X| >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Build Time (ms)} & \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Ranker Prediction Time (ms)} \\ \cline{2-9}
										& Min		& Max		& Mean		& Stdv 	& Min	& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	& 0 		& 1      	& 0	 	    & 0 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	& 0 		& 16		 	& 0	 		& 1	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	& 0		& 16 		& 3	 		& 2	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	& 0 		& 16			& 1	 		& 16	\\	
		InstanceBased 					& 66 		& 550 		& 90	 		& 25 	& 0 		& 47			& 5 			& 8	\\	
		InstanceBased\footnotemark{}		& 66 		& 138 		& 88	 		& 12 	& 0 		& 19		 	& 1			& 3	\\	
		InstanceBased\footnotemark{}		& 66 		& 163		& 87	 		& 12 	& 0 		& 16		 	& 1		 	& 2	\\	
		PairwiseComparison 				& 11784 		& 15096		& 12623	 	& 348 	& 0 		& 0 			& 9.762	 	& 13.135	\\	
		BestAlgorithm	 				& 193	 	& 321		& 221	 	& 23	 	& 0		& 0			&  0 		& 0\\							
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Build and Prediction Times of the Rankers rounded to Full Milliseconds (Full Meta Data)}
\end{table}

%TODO add values for pairwise comparision}
\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}

@@

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\hsize=1.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X | >{\hsize=.8\hsize}X}
		Ranker 				& \multicolumn{4}{>{\hsize=4.0\hsize\centering\arraybackslash}X}{Root Mean Square Error} \\ \cline{2-5}
										& Min		& Max		& Mean		& Stdv 	\\ \hline
		LinearRegression 				& 1454 		& 2060 		& 1580	 	& 36 	\\
		M5P				 				& 3145 		& 4916 		& 3226	 	& 89 	\\	
		RandomForest		 				& 6048 		& 9720 		& 6236	 	& 259 	\\	
		REPTree			 				& 599 		& 1264 		& 629		& 38 	\\								
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Root Mean Square Error of Predicted Performance Values for the Regression-Based Rankers (full meta data)}
\end{table}

% TODO replace by large data set??
\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X}
		%\hline
		Classifier				&	Number of Data Sets Placed First \\	\hline
		Logistic					&	28								\\	\hline	
		Naive Bayes				&	29								\\	\hline	
		IBk						&	23								\\	\hline	
		KStar					&	24								\\	\hline	
		LMT						&	17								\\	\hline	
		VotedPerceptron			&	16								\\	\hline	
		ZeroR					&	14								\\	\hline	
		J48						&	13								\\	\hline	
		NaiveBayesMultinomial	&	6								\\	\hline	
		RandomTree				&	2								\\	\hline	
		SimpleLogistic			&	1								\\	\hline
		DecisionStump			&	1								\\	\hline
		MultilayerPerceptron		&	1								\\	\hline
		RandomForest				&	1								\\	\hline
		DecisionTable			&	1								\\	\hline
		PART						&	1								\\	\hline
		SGD						&	1								\\	\hline
		BayesNet					&	1								\\	\hline
		REPTree					&	1								\\	\hline
		JRip						&	1								\\	\hline
		SMO						&	313								\\	\hline
		OneR						&	448								\\	\hline																	
	\end{tabularx}
	\label{tab:table1}
	\caption{The ranking of Classifiers returned by the Best Algorithm Baseline}
\end{table}

>>>>

This chapter is dedicated to the evaluation of the proposed ranking approaches. First, the oracle and baseline against which the rankers are compared are explained. Second, the experimental setup, that is conditions under which the evaluation was conducted, is set forth. Last, results are presented and discussed.

@@

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{chapter:fundamentals}. These include the Kendall rank correlation coefficient, loss and best three loss. The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic of the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline. More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented. That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth. This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot bet computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significant better than the baseline, which will be determined by calculating the Mann-Whitney U and determining whether its P-value.

@@

% Gathering data sets from OpenML
how many data sets from OpenML

% Generating base performance data
Performance Values acquired with 5 times MCCV
which (hyper)parameters where used
which timeouts used
why decided to use these algorithms and not others

@@

\input{tables/evaluationResults}
\ref{tab:evaluationResults}

\input{tables/metaFeatureTimes}
\ref{tab:metaFeatureTimes}

\input{tables/significanceResults}
\ref{tab:significanceResults}

@@

\subsection{Build and Prediction Times}

\input{tables/times}
\ref{tab:times}
%TODO add values for pairwise comparision in this table

@@

\input{tables/rootMeanSquareError}
\ref{tab:rootMeanSquareError}

\input{tables/bestAlgorithmRanking}
\ref{tab:bestAlgorithmRanking}
